Methods for Large Scale Learning to Rank

### 2014-02-21 report/Chapters/Introduction.tex
referenties opgeschoond + definitie speed-up

\chapter{Research Goals}
\label{chap:goals}
The objective of this thesis is to explore the speed-up in execution time of Learning-to-Rank algorithms through parallelisation using the MapReduce framework. 
This work focuses on those Learning-to-Rank algorithms that have shown leading performance on relevant benchmark datasets.
The research questions raised and answered in this work include:
\begin{itemize}
\item What is the speed-up of existing Learning-to-Rank algorithms when executed using the MapReduce framework?
\item Can we adjust those Learning-to-Rank algorithms such that the parallel execution speed-up increases without decreasing accuracy?
\end{itemize}

>>>>

\chapter{Research Goals}
\label{chap:goals}
The objective of this thesis is to explore the speed-up in execution time of Learning-to-Rank algorithms through parallelisation using the MapReduce framework. 
This work focuses on those Learning-to-Rank algorithms that have shown leading performance on relevant benchmark datasets.
The research questions raised and answered in this work include:
\begin{itemize}
\item What is the speed-up of existing Learning-to-Rank algorithms when executed using the MapReduce framework?\\
In which Nussbaum and Agarwal's definition of asymptotic speed-up will be used for speed-up $S(s)$\cite{Nussbaum1991}:\\

\begin{math}
s \equiv \text{problem size}\\
T_{seq}(s) \equiv \Theta(\text{Serial Running Time})\\
T_{par}(s) \equiv \Theta(\text{Minimum Parallel Running Time})\\
S(s) \equiv \frac{T_{seq}(s)}{T_{par}(s)}\\
\end{math}

\item Can we adjust those Learning-to-Rank algorithms such that the parallel execution speed-up increases without decreasing accuracy?
\end{itemize}
